WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-07 lit/sec_2-lead.tex
v5.0
replace with weather forecast

The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-OrientedWeather}:
\begin{itemize}
    \item the users interact with LEAD via a Web portal
    \item data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
    \item myLEAD is the metadata catalog
    \item Weather Research and Forecast \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
    \item Algorithm Development and Mining is a set of tools for analyzing observational data, assimilated data sets, and model output
    \item Integrated Data Viewer 
\end{itemize}

@@

LEAD is a more advanced system which can support mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources. At the time of  building, it uses the \acrshort{soa} architecture into its depth, and at the implementation, each service can scale as needed and possible to enhance the service without interrupting other services. However, during our research, we only focus on creating a framework that is extendable as a system needs more features similar to LEAD services.

>>>>

The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-OrientedWeather}:
\begin{itemize}
    \item The users interact with LEAD via a Web portal
    \item Data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
    \item myLEAD is the metadata catalog
    \item Weather Research and Forecast \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
    \item Algorithm Development and Mining is a set of tools for analyzing observational data, assimilated data sets, and model output
    \item Integrated Data Viewer 
\end{itemize}

@@

LEAD is a more advanced system which can support mesoscale weather forecast with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources. At the time of  building, it uses the \acrshort{soa} architecture into its depth, and at the implementation, each service can scale as needed and possible to enhance the service without interrupting other services. However, during our research, we only focus on creating a framework that is extendable as a system needs more features similar to LEAD services.
